---
title: "Recreating Figures 9 and 10 in the manuscript: When should we collapse cells for Multilevel Regression and Poststratification?"
author: "Yuxiang Gao"
date: "10/09/2021"
output: html_document
---

# Figure 9 caption:

Target estimand is the population mean, which in this case is 0. Variance terms 1,2,3 are the first, second and third terms in Equation 8. The total is the sum of the three terms. They are evaluated across J income groups, where J = 3, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100. The main survey sample size (top facet label) ranges from left plot to right plot. The auxiliary survey size is 825, which is around 0.6 percent of the target population. Each subplot uses 3 main survey samples of different representativeness across all the settings of J.

# Figure 10 caption:

Target estimand is the subpopulation mean for the male individuals in the fourth age group. This subgroup size is 4.6 percent of the target population. Variance terms 1,2,3 are the first, second and third terms in Equation 14. The total is the sum of the three terms. They are evaluated across J income groups, where J = 3, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100. The main survey sample size (top facet label) ranges from left plot to right plot. The auxiliary survey size is 825, which is around 0.6 percent of the target population. Each subplot uses 3 main survey samples of different representativeness across all the settings of J.

## Put the packages in

```{r, message = FALSE}
seed_num = 420001
set.seed(seed_num)
library(tidyverse)
library(brms)
library(tidybayes)
library(survey)

age_fivegroups_target = 4
sex_binary_target = 0
p = 0.9 # p determines how nonrepresentative D is

# Dsize is nonrep sample size
Dsize = 1000
# ACSstratasize is the size of random sample in each PUMA strata when performing a stratified random sample of P
ACSstratasize = 15
```

## Construct D2 like we did initially. Also add sex, race, edu, age to population P

```{r}
nystate = readRDS("nystate_fiveyear2015_2019.rds")

# five counties in new york city
P = nystate %>% 
  filter(COUNTYFIP %in% c(61,47,81,5,85) & 
           (RENT > 0) & 
           (INCTOT > 0) & 
           !(INCTOT %in% c(9999998,9999999))) %>% 
  select(RENT, INCTOT, PUMA, SEX, AGE, RACE, EDUC)

# make age into 5 categories, race into 5 categories, educational attainment into 5 categories, sex as binary variable
P  = P %>% mutate(
  age_fivegroups = cut(
    P$AGE,
    breaks = c(min(P$AGE),21,40,65,80,max(P$AGE)),
    include.lowest = TRUE,
    labels = 1:5),
  race_fivegroups = case_when(RACE == 1 ~ 1,
                              RACE == 2 ~ 2,
                              RACE == 3 ~ 3,
                              RACE %in% c(4,5,6) ~ 4,
                              RACE %in% c(7,8,9) ~ 5),
  edu_fivegroups = case_when(EDUC == 0 ~ 1,
                             EDUC %in% c(1,2) ~ 2,
                             EDUC %in% c(3,4,5,6) ~ 3,
                             EDUC %in% c(7,8,9,10) ~ 4,
                             EDUC == 11 ~ 5),
  sex_binary = case_when(SEX == 1 ~ 0,
                         SEX == 2 ~ 1)
)

# convert covariates to factors 
P$age_fivegroups = as.factor(P$age_fivegroups)
P$race_fivegroups = as.factor(P$race_fivegroups)
P$edu_fivegroups = as.factor(P$edu_fivegroups)


P$index = 1:(dim(P)[1])

P$logRENTcentered = log(P$RENT) - mean(log(P$RENT))


# get population sizes of PUMA in P
P_PUMAsize = P %>% group_by(PUMA) %>% summarise(N = n()) %>% mutate(fraction = N/sum(N))

# Define probs to do PPSWOR for D2
P$INCTOTprobD2 = 0
P[P$INCTOT<=median(P$INCTOT), c("INCTOTprobD2")] = p
P[P$INCTOT>median(P$INCTOT), c("INCTOTprobD2")] = 1-p

# create response vector for every individual in P as a function of age and sex
P$response_prob = arm::invlogit(0.02*P$AGE + 0.05*P$sex_binary)

# sample D2
D2indices = sample(x=1:dim(P)[1],
                   prob=P$INCTOTprobD2,
                   replace=FALSE,
                   size=Dsize)

D2 = P[D2indices,]

# ACS sample S without inclusion probs and defining incomebracket ####
pseudoACS_unweighted_beforeloop = c()

# Stage 1: Get stratified sample pseudoACS_unweighted, where strata are PUMA. Sampled according to relative size of PUMA
# Stage 2: Now add nonresponse according to P$response_prob
for (PUMA_ in P_PUMAsize$PUMA) {
  pseudoACS_unweighted_beforeloop = rbind(pseudoACS_unweighted_beforeloop,
                                          P %>% filter(PUMA==PUMA_) %>% 
                                            sample_n( size = round((ACSstratasize * 55) * 
                                                                     (P_PUMAsize %>% filter(PUMA==PUMA_) %>% select(fraction) %>% as.numeric)),
                                                      weight = response_prob,
                                                      #weight = 1,
                                                      replace=FALSE
                                            )
  )
}



rm(D2indices,nystate,PUMA_)
gc()

summary(D2$INCTOT)

D2 %>% filter(age_fivegroups==age_fivegroups_target, sex_binary==sex_binary_target) %>% summarise(mean(logRENTcentered), sd(logRENTcentered)/sqrt(n()),n())
P %>% filter(age_fivegroups==age_fivegroups_target, sex_binary==sex_binary_target) %>% summarise(mean(logRENTcentered), sd(logRENTcentered)/sqrt(n()))
```

## Pull in the data and fix things

```{r}

main_survey <- D2 %>% mutate(logRent = RENT, 
                             logINCTOT = log(INCTOT))
population <- P %>% mutate(logRent = RENT, 
                           logINCTOT = log(INCTOT))
aux_survey <- pseudoACS_unweighted_beforeloop %>% 
  mutate(logRent = RENT, 
         logINCTOT = log(INCTOT)) %>%
  left_join(P_PUMAsize, by = "PUMA") %>%
  rename(puma_size = N)
rm(D2, P, pseudoACS_unweighted_beforeloop, P_PUMAsize)
gc()
```

## Do this for a single J

```{r, message = FALSE}
mrp_sd <- function(J, 
                   main_survey_ = main_survey, 
                   aux_survey_ = aux_survey, 
                   population_ = population,
                   target_age_group = age_fivegroups_target,
                   target_sex_binary = sex_binary_target){
  ## make the income_level variable
  main_survey_ <- main_survey_ %>% mutate(
    income_bracket = cut(
      main_survey_$INCTOT,
      breaks=quantile(population_$INCTOT, 
                      probs = seq(0,1,by=1/J)),
      include.lowest = TRUE,
      labels = 1:J)
  )
  
  aux_survey_<- aux_survey_ %>% mutate(
    income_bracket = cut(
      aux_survey_$INCTOT,
      breaks = quantile(population_$INCTOT,
                        probs = seq(0,1,by = 1/J)),
      include.lowest = TRUE,
      labels = 1:J)
  )
    
  
  ## not needed, just for checking against correct Nj
  population_ <- population_ %>% mutate(
    income_bracket = cut(
      population_$INCTOT,
      breaks = quantile(population_$INCTOT,
                        probs = seq(0,1,by = 1/J)),
      include.lowest = TRUE,
      labels = 1:J)
  )
  
  poststrat_true <- right_join((population_ %>% 
                                  group_by(sex_binary,
                                           income_bracket, 
                                           age_fivegroups) %>%
                                  summarise(Nj = n()) %>%
                                  ungroup()
  ),
  tibble(expand.grid(sex_binary = c(0,1),
                     income_bracket = factor(1:J),
                     age_fivegroups = factor(1:5)), zero = 0),
  by = c("sex_binary", "income_bracket", "age_fivegroups"))
  
  poststrat_true$Nj[is.na(poststrat_true$Nj)] = 0
  
  
  ## Estimate Nj_hat from the aux survey and compute covariance matrix
  margins <- population_ %>% group_by(PUMA) %>% summarise(Freq=n())
  margins_sex = population_ %>% group_by(sex_binary) %>% summarise(Freq = n())
  margins_age_fivegroups = population_ %>% group_by(age_fivegroups) %>% summarise(Freq=n())
  
  # initialize aux survey as stratified random sample
  aux_design <- svydesign(id = ~1,
                          strata = ~PUMA,
                          data = aux_survey_,
                          fpc = ~puma_size)



  aux_rake <- rake(design = aux_design,
                   list(~PUMA,
                        ~sex_binary,
                        ~age_fivegroups
                   ),
                   list(margins,
                        margins_sex,
                        margins_age_fivegroups
                   ))
  

  

  Nj_hat <- svytotal(~interaction(sex_binary,
                                  income_bracket, 
                                  age_fivegroups),
                     aux_rake)
  gc()
  #Nj_hat <- svytable(~income_bracket + age_fivegroups + edu_fivegroups + race_fivegroups, aux_rake)
  
  Nj_cov <- vcov(Nj_hat)
  
  
  
  poststrat <- Nj_hat %>%
    coef %>%
    enframe %>% mutate(Nj_hat = value)
  
  rm(Nj_hat)
  gc()
  
  poststrat$sex_binary = lapply(str_match_all(poststrat$name,"[0-9]+"), FUN = function(x) {(as.numeric(x))[1]}) %>% unlist
  poststrat$income_bracket = lapply(str_match_all(poststrat$name,"[0-9]+"), FUN = function(x) {(as.numeric(x))[2]}) %>% unlist
  poststrat$age_fivegroups = lapply(str_match_all(poststrat$name,"[0-9]+"), FUN = function(x) {(as.numeric(x))[3]}) %>% unlist

  
  ## Estimate multilevel model
  bye <-capture.output(
  mod <- brm(formula = logRENTcentered ~ sex_binary + (1 | income_bracket) + (1 | age_fivegroups),
             prior = c(
               prior(normal(0, 5), class=Intercept), # change sd to 2
               prior(normal(0, 5), class = sd),
               prior(normal(0, 5), class = sigma),
               prior(normal(0, 5), class = b)
             ),
             data = main_survey_,
             chains=1,
             cores=1,
             refresh = 0,
             backend = "cmdstanr",
             control = list(adapt_delta = 0.95)
            
  ), type = "output")
  gc()
  
  ## Poststrat (both with Nj and Nj_hat just for checking)
  prediction <- posterior_linpred(mod, 
                                  newdata = poststrat,
                                  allow_new_levels = TRUE)
  
  prediction_ps <- apply( prediction, 1, function(x){
    sum(poststrat$Nj_hat * x) / sum(poststrat$Nj_hat)
  })
  
  prediction_ps_true <- apply( prediction, 1, function(x){
    sum(poststrat_true$Nj * x) / sum(poststrat_true$Nj)
  })
  
  
  ## Organise the output
  N <- length(population_$logRENTcentered)
  theta_mean <- colMeans(prediction)
  theta_cov <- cov(prediction)
  
  # Subgroup analysis for age group defined by target_age_group ####
  poststrat$index = 1:dim(poststrat)[1]
  
  subgroup_poststrat_indices = poststrat %>% 
    filter(age_fivegroups == target_age_group, sex_binary == target_sex_binary) %>% 
    select(index) %>% unlist()
  
  # https://cran.r-project.org/web/packages/survey/vignettes/domain.pdf  
  # https://stats.stackexchange.com/questions/411026/why-it-is-important-to-make-survey-design-object-svydesign-function-in-r-with-i
  aux_rake_subset = subset(aux_rake, age_fivegroups == target_age_group & sex_binary == target_sex_binary)
  
  
  Nj_over_N_hat_subpop = svymean(~interaction(sex_binary, income_bracket, age_fivegroups),
                                 aux_rake_subset)
  gc()
  
  # get poststrat proportions for subgroup
  subpop_proportions = Nj_over_N_hat_subpop %>% coef %>% enframe %>% mutate(Nj_over_N_hat = value)
  
  subpop_proportions$sex_binary = lapply(str_match_all(subpop_proportions$name,"[0-9]+"), FUN = function(x) {(as.numeric(x))[1]}) %>% unlist
  subpop_proportions$income_bracket = lapply(str_match_all(subpop_proportions$name,"[0-9]+"), FUN = function(x) {(as.numeric(x))[2]}) %>% unlist
  subpop_proportions$age_fivegroups = lapply(str_match_all(subpop_proportions$name,"[0-9]+"), FUN = function(x) {(as.numeric(x))[3]}) %>% unlist

  subpop_proportions = subpop_proportions %>% filter(age_fivegroups == target_age_group & sex_binary == target_sex_binary)
  
  Nj_over_N_cov = vcov(Nj_over_N_hat_subpop)[subgroup_poststrat_indices, subgroup_poststrat_indices]
  
  
  prediction_subgroup = posterior_linpred(mod, 
                                          newdata = poststrat[subgroup_poststrat_indices,],
                                          allow_new_levels = TRUE)
  
  prediction_ps_subgroup <- apply(prediction_subgroup, 1, function(x){
    sum(poststrat[subgroup_poststrat_indices,]$Nj_hat * x) / sum(poststrat[subgroup_poststrat_indices,]$Nj_hat)
  })
  
  #########
  
  
  prediction_ps_true_subgroup <- apply( prediction_subgroup, 1, function(x){
    sum(poststrat_true[subgroup_poststrat_indices,]$Nj * x) / sum(poststrat_true[subgroup_poststrat_indices,]$Nj)
  })
  
  
  # output what we estimated
  tibble(mean_logRENT = mean(prediction_ps),
         mean_logRENT_true = mean(prediction_ps_true),
         var_logRENT_true = var(prediction_ps_true),
         var_logRENT = var(prediction_ps),
         term1 = sum(diag(theta_cov %*% Nj_cov)) / N^2,
         term2 = (t(poststrat$Nj_hat) %*% theta_cov %*% poststrat$Nj_hat) / N^2,
         term3 = (t(theta_mean) %*% Nj_cov %*% theta_mean) / N^2,
         total = term1 + term2 + term3,
         population_level_var = (summary(mod)[["spec_pars"]][1])^2,
         age_grouplevel_var = (summary(mod)[["random"]]$age_fivegroups[1])^2,
         income_grouplevel_var = (summary(mod)[["random"]]$income_bracket[1])^2,
         maxeigen_theta_cov = max(eigen(theta_cov)$values),
         twonormsquared_poststratweights = sum((poststrat$Nj_hat/sum(poststrat$Nj_hat))^2),
         twonormsquared_poststratweights_known = sum((poststrat_true$Nj/sum(poststrat_true$Nj))^2),
         sharp_upper_bound = maxeigen_theta_cov * twonormsquared_poststratweights,
         
         term1_subgroup = sum(diag(theta_cov[subgroup_poststrat_indices, subgroup_poststrat_indices] %*% Nj_over_N_cov)),
         term2_subgroup = var(prediction_ps_subgroup),
         term3_subgroup = (t(theta_mean[subgroup_poststrat_indices]) %*% Nj_over_N_cov %*% theta_mean[subgroup_poststrat_indices]) / (sum(poststrat[subgroup_poststrat_indices,]$Nj_hat))^2,
         
         maxeigen_theta_cov_subgroup = max(eigen(theta_cov[subgroup_poststrat_indices, subgroup_poststrat_indices])$values),
         twonormsquared_poststratweights_subgroup = sum((poststrat[subgroup_poststrat_indices,]$Nj_hat/sum(poststrat[subgroup_poststrat_indices,]$Nj_hat))^2),
         twonormsquared_poststratweights_known_subgroup = sum((poststrat_true[subgroup_poststrat_indices,]$Nj/sum(poststrat_true[subgroup_poststrat_indices,]$Nj))^2),
         sharp_upper_bound_subgroup = maxeigen_theta_cov_subgroup * twonormsquared_poststratweights_subgroup
         )
}

mrp_sd(10)

```


## Ok now let's run it 

```{r, message = FALSE, warning = FALSE}

est <- tibble(J = c(3,10,20,30,40,50,60,70,80,90,100)) %>%
  mutate(out = purrr::map(J, mrp_sd)) %>% 
  unnest(out)

         
saveRDS(est, file = paste0("est_",
                           seed_num,
                           "_",
                           Dsize,
                           "_",
                           ACSstratasize,
                           "_",
                           p*100,
                           "_",
                           age_fivegroups_target,
                           "_",
                           sex_binary_target,
                           ".rds"))

```

## Make a plot

Notation:

term1: $\frac{1}{N^2}  {\text{tr}} \left( {\Sigma_{\theta \mid \mathcal{D}}} \hat{{\Sigma}}_{J,N} \right)$

term2: $\frac{1}{N^2} \vec{\hat{N}}^T {\Sigma_{\theta \mid \mathcal{D}}} \vec{\hat{N}}$

term3: $\frac{1}{N^2} {\hat{\Theta}_{J}}^T \hat{{\Sigma}}_{J,N} {\hat{\Theta}_{J}}$

maxeigen theta cov: $\lambda_\text{max} \left( \Sigma_{\theta | \mathcal{D}}  \right)$

twonormsquared poststratweights : $|| \frac{\vec{\hat{N}}}{\hat{N}^2} ||_2^2$

twonormsquared poststratweights known: $|| \frac{\vec{{N}}}{{N}^2} ||_2^2$

sharp upper bound: $|| \frac{\vec{\hat{N}}}{\hat{N}^2} ||_2^2 \lambda_\text{max} \left( \Sigma_{\theta | \mathcal{D}}  \right)$

upperbound true: $|| \frac{\vec{{N}}}{{N}^2} ||_2^2 \lambda_\text{max} \left( \Sigma_{\theta | \mathcal{D}}  \right)$

```{r}
est$upperbound_true = est$twonormsquared_poststratweights_known * est$maxeigen_theta_cov
est$upperbound_true_subgroup = est$twonormsquared_poststratweights_known_subgroup * est$maxeigen_theta_cov_subgroup

est %>% pivot_longer(-c(J, mean_logRENT, mean_logRENT_true)) %>% 
  filter(!(name %in% c("age_grouplevel_var",
                       "income_grouplevel_var", 
                       "population_level_var",
                       "var_logRENT",
                       "var_logRENT_true",
                       "term1_subgroup",
                       "term2_subgroup",
                       "term3_subgroup",
                       "maxeigen_theta_cov_subgroup",
                       "twonormsquared_poststratweights_subgroup",
                       "twonormsquared_poststratweights_known_subgroup",
                       "sharp_upper_bound_subgroup",
                       "upperbound_true_subgroup",
                       "total"
                       ))) %>% 
  ggplot(aes(x = J, y = value, colour = name)) +
  geom_line() + scale_y_log10() + 
  ylab("log-scaled variance term") + 
  ggtitle("population estimand")
```

```{r}
est %>% pivot_longer(-c(J, mean_logRENT, mean_logRENT_true)) %>% 
  filter((name %in% c(
                       "term1_subgroup",
                       "term2_subgroup",
                       "term3_subgroup",
                       "maxeigen_theta_cov_subgroup",
                      "twonormsquared_poststratweights_subgroup",
                       "twonormsquared_poststratweights_known_subgroup",
                       "sharp_upper_bound_subgroup",
                       "upperbound_true_subgroup"
                       ))) %>% 
  ggplot(aes(x = J, y = value, colour = name)) +
  geom_line() + scale_y_log10() + 
  ylab("log-scaled variance term") + 
  ggtitle(("subpop estimand"))
```

## A potential reason for why $\frac{1}{\hat{N}^2} \vec{\hat{N}}^T {\Sigma_{\theta \mid \mathcal{D}}} \vec{{\hat{N}}}$ is constant across $J$

The sharp upper bound below is nearly constant across $J$ from the above plot.

$\begin{equation}
        \begin{aligned}
          \frac{1}{\hat{N}^2} \vec{\hat{N}}^T {\Sigma_{\theta \mid \mathcal{D}}} \vec{{\hat{N}}} &\le \left|\left| \frac{\vec{\hat{N}}}{\hat{N}^2} \right|\right|_2^2 \lambda_\text{max} \left( \Sigma_{\theta | \mathcal{D}}  \right)
        \end{aligned}
\end{equation}$

When $\vec{\hat{N}}$ is replaced by $\vec{{N}}$, the upper bound becomes constant.

# The below chunk of code creates Figure 9, 10 after the following files have been generated:

$\text{est_420002_1000_15_90_4_0.rds}$

$\text{est_420002_1000_15_75_4_0.rds}$

$\text{est_420002_1000_15_50_4_0.rds}$

$\text{est_420002_2000_15_90_4_0.rds}$

$\text{est_420002_2000_15_75_4_0.rds}$

$\text{est_420002_2000_15_50_4_0.rds}$

```{r,eval = FALSE}



est_p90 = readRDS("est_420002_1000_15_90_4_0.rds")
est_p75 = readRDS("est_420002_1000_15_75_4_0.rds")
est_p50 = readRDS("est_420002_1000_15_50_4_0.rds")

est_p90_2000 = readRDS("est_420002_2000_15_90_4_0.rds")
est_p75_2000 = readRDS("est_420002_2000_15_75_4_0.rds")
est_p50_2000 = readRDS("est_420002_2000_15_50_4_0.rds")

est_p90_4000 = readRDS("est_420002_4000_15_90_4_0.rds")
est_p75_4000 = readRDS("est_420002_4000_15_75_4_0.rds")
est_p50_4000 = readRDS("est_420002_4000_15_50_4_0.rds")

est_p90$upperbound_true = est_p90$twonormsquared_poststratweights_known * est_p90$maxeigen_theta_cov
est_p90$upperbound_true_subgroup = est_p90$twonormsquared_poststratweights_known_subgroup * est_p90$maxeigen_theta_cov_subgroup
est_p90$total_subgroup = rowSums(est_p90[,c("term1_subgroup",
                                            "term2_subgroup",
                                            "term3_subgroup"
)])

est_p75$upperbound_true = est_p75$twonormsquared_poststratweights_known * est_p75$maxeigen_theta_cov
est_p75$upperbound_true_subgroup = est_p75$twonormsquared_poststratweights_known_subgroup * est_p75$maxeigen_theta_cov_subgroup
est_p75$total_subgroup = rowSums(est_p75[,c("term1_subgroup",
                                            "term2_subgroup",
                                            "term3_subgroup"
)])

est_p50$upperbound_true = est_p50$twonormsquared_poststratweights_known * est_p50$maxeigen_theta_cov
est_p50$upperbound_true_subgroup = est_p50$twonormsquared_poststratweights_known_subgroup * est_p50$maxeigen_theta_cov_subgroup
est_p50$total_subgroup = rowSums(est_p50[,c("term1_subgroup",
                                            "term2_subgroup",
                                            "term3_subgroup"
)])


est_p90_2000$upperbound_true = est_p90_2000$twonormsquared_poststratweights_known * est_p90_2000$maxeigen_theta_cov
est_p90_2000$upperbound_true_subgroup = est_p90_2000$twonormsquared_poststratweights_known_subgroup * est_p90_2000$maxeigen_theta_cov_subgroup
est_p90_2000$total_subgroup = rowSums(est_p90_2000[,c("term1_subgroup",
                                                      "term2_subgroup",
                                                      "term3_subgroup"
)])

est_p75_2000$upperbound_true = est_p75_2000$twonormsquared_poststratweights_known * est_p75_2000$maxeigen_theta_cov
est_p75_2000$upperbound_true_subgroup = est_p75_2000$twonormsquared_poststratweights_known_subgroup * est_p75_2000$maxeigen_theta_cov_subgroup
est_p75_2000$total_subgroup = rowSums(est_p75_2000[,c("term1_subgroup",
                                                      "term2_subgroup",
                                                      "term3_subgroup"
)])

est_p50_2000$upperbound_true = est_p50_2000$twonormsquared_poststratweights_known * est_p50_2000$maxeigen_theta_cov
est_p50_2000$upperbound_true_subgroup = est_p50_2000$twonormsquared_poststratweights_known_subgroup * est_p50_2000$maxeigen_theta_cov_subgroup
est_p50_2000$total_subgroup = rowSums(est_p50_2000[,c("term1_subgroup",
                                                      "term2_subgroup",
                                                      "term3_subgroup"
)])

est_p90_4000$upperbound_true = est_p90_4000$twonormsquared_poststratweights_known * est_p90_4000$maxeigen_theta_cov
est_p90_4000$upperbound_true_subgroup = est_p90_4000$twonormsquared_poststratweights_known_subgroup * est_p90_4000$maxeigen_theta_cov_subgroup
est_p90_4000$total_subgroup = rowSums(est_p90_4000[,c("term1_subgroup",
                                                      "term2_subgroup",
                                                      "term3_subgroup"
)])

est_p75_4000$upperbound_true = est_p75_4000$twonormsquared_poststratweights_known * est_p75_4000$maxeigen_theta_cov
est_p75_4000$upperbound_true_subgroup = est_p75_4000$twonormsquared_poststratweights_known_subgroup * est_p75_4000$maxeigen_theta_cov_subgroup
est_p75_4000$total_subgroup = rowSums(est_p75_4000[,c("term1_subgroup",
                                                      "term2_subgroup",
                                                      "term3_subgroup"
)])

est_p50_4000$upperbound_true = est_p50_4000$twonormsquared_poststratweights_known * est_p50_4000$maxeigen_theta_cov
est_p50_4000$upperbound_true_subgroup = est_p50_4000$twonormsquared_poststratweights_known_subgroup * est_p50_4000$maxeigen_theta_cov_subgroup
est_p50_4000$total_subgroup = rowSums(est_p50_4000[,c("term1_subgroup",
                                                      "term2_subgroup",
                                                      "term3_subgroup"
)])

est_combined = rbind(tibble(est_p90, Dsize = 1000, ACSstratasize = 15*55, p = "Very nonrepresentative"),
                     tibble(est_p75, Dsize = 1000, ACSstratasize = 15*55, p = "Nonrepresentative"),
                     tibble(est_p50, Dsize = 1000, ACSstratasize = 15*55, p = "Representative"),
                     tibble(est_p90_2000, Dsize = 2000, ACSstratasize = 15*55, p = "Very nonrepresentative"),
                     tibble(est_p75_2000, Dsize = 2000, ACSstratasize = 15*55, p = "Nonrepresentative"),
                     tibble(est_p50_2000, Dsize = 2000, ACSstratasize = 15*55, p = "Representative"),
                     tibble(est_p90_4000, Dsize = 4000, ACSstratasize = 15*55, p = "Very nonrepresentative"),
                     tibble(est_p75_4000, Dsize = 4000, ACSstratasize = 15*55, p = "Nonrepresentative"),
                     tibble(est_p50_4000, Dsize = 4000, ACSstratasize = 15*55, p = "Representative")
)

est_combined$p = factor(est_combined$p)
est_combined$p = factor(est_combined$p, levels = c("Representative",
                                                   "Nonrepresentative",
                                                   "Very nonrepresentative"))

colnames(est_combined)[colnames(est_combined)=="term1"] = "Variance term 1"
colnames(est_combined)[colnames(est_combined)=="term2"] = "Variance term 2"
colnames(est_combined)[colnames(est_combined)=="term3"] = "Variance term 3"
colnames(est_combined)[colnames(est_combined)=="sharp_upper_bound"] = "Upper bound"
colnames(est_combined)[colnames(est_combined)=="p"] = "Main survey data type"

colnames(est_combined)[colnames(est_combined)=="total"] = "Total"









est_combined %>% pivot_longer(-c(J, mean_logRENT, mean_logRENT_true,Dsize,ACSstratasize,`Main survey data type`)) %>% 
  filter(!(name %in% c("age_grouplevel_var",
                       "income_grouplevel_var", 
                       "population_level_var",
                       "var_logRENT",
                       "var_logRENT_true",
                       "term1_subgroup",
                       "term2_subgroup",
                       "term3_subgroup",
                       "maxeigen_theta_cov_subgroup",
                       "twonormsquared_poststratweights_subgroup",
                       "twonormsquared_poststratweights_known_subgroup",
                       "sharp_upper_bound_subgroup",
                       "upperbound_true_subgroup",
                       "total_subgroup",
                       "twonormsquared_poststratweights_known",
                       "upperbound_true",
                       "twonormsquared_poststratweights",
                       "maxeigen_theta_cov"
  ))) %>% 
  ggplot(aes(x = J, y = value, colour = name)) +
  geom_line(size=1,aes(linetype=`Main survey data type`)) + facet_grid(.~Dsize) +
  scale_y_log10() + 
  ylab("log-scaled variance term") + 
  ggtitle("") + 
  theme_minimal() +
  theme(legend.position="bottom",
        legend.box="vertical",
        text = element_text(size=25),
        axis.text.x = element_text(angle=45, hjust=1),
        strip.text.x = element_text(size = 25),
        strip.text.y = element_text(size = 25),
        legend.title = element_text(size = 25),
        panel.spacing = unit(2, "lines")
  ) + labs(color='Variance term') + scale_colour_manual(values=c("Total"="#D55E00",
                                                                 "Upper bound" = "#56B4E9",
                                                                 "Variance term 1"= "#009E73",
                                                                 "Variance term 2"="#0072B2",
                                                                 "Variance term 3"="#CC79A7"))

ggsave(paste0("population_3_100.png"), width = 24, height = 12)






colnames(est_combined)[colnames(est_combined)=="term1_subgroup"] = "Variance term 1 subgroup"
colnames(est_combined)[colnames(est_combined)=="term2_subgroup"] = "Variance term 2 subgroup"
colnames(est_combined)[colnames(est_combined)=="term3_subgroup"] = "Variance term 3 subgroup"
colnames(est_combined)[colnames(est_combined)=="sharp_upper_bound_subgroup"] = "Upper bound subgroup"
colnames(est_combined)[colnames(est_combined)=="total_subgroup"] = "Total subgroup"




est_combined %>% pivot_longer(-c(J, mean_logRENT, mean_logRENT_true,Dsize,ACSstratasize,`Main survey data type`)) %>% 
  filter(!(name %in% c("age_grouplevel_var",
                       "income_grouplevel_var", 
                       "population_level_var",
                       "var_logRENT",
                       "var_logRENT_true",
                       "Variance term 1",
                       "Variance term 2",
                       "Variance term 3",
                       "maxeigen_theta_cov_subgroup",
                       "twonormsquared_poststratweights_subgroup",
                       "twonormsquared_poststratweights_known_subgroup",
                       "sharp_upper_bound_subgroup",
                       "upperbound_true_subgroup",
                       "Total",
                       "twonormsquared_poststratweights_known",
                       "upperbound_true",
                       "twonormsquared_poststratweights",
                       "maxeigen_theta_cov",
                       "Upper bound"
  ))) %>% 
  ggplot(aes(x = J, y = value, colour = name)) +
  geom_line(size=1, aes(linetype=`Main survey data type`)) + facet_grid(.~Dsize) +
  scale_y_log10() + 
  ylab("log-scaled variance term") + 
  ggtitle("") + 
  theme_minimal() +
  theme(legend.position="bottom",
        legend.box="vertical",
        text = element_text(size=25),
        axis.text.x = element_text(angle=45, hjust=1),
        strip.text.x = element_text(size = 25),
        strip.text.y = element_text(size = 25),
        legend.title = element_text(size = 25),
        panel.spacing = unit(2, "lines")
  ) + labs(color='Variance term') + scale_colour_manual(values=c("Total subgroup"="#D55E00",
                                                                 "Upper bound subgroup" = "#56B4E9",
                                                                 "Variance term 1 subgroup"= "#009E73",
                                                                 "Variance term 2 subgroup"="#0072B2",
                                                                 "Variance term 3 subgroup"="#CC79A7"))

ggsave(paste0("subpopulation_0_4_3_100.png"), width = 24, height = 12)
```


