---
title: "Adding sex and age to the simulation"
author: "Alex Gao"
date: "10/09/2021"
output: html_document
---
## Put the packages in

```{r, message = FALSE}
seed_num = 420001
set.seed(seed_num)
library(tidyverse)
library(brms)
library(tidybayes)
library(survey)

age_fivegroups_target = 4
sex_binary_target = 0
p = 0.9 # p determines how nonrepresentative D is
```

## Construct D2 like we did initially. Also add sex, race, edu, age to population P

```{r}
nystate = readRDS("nystate_fiveyear2015_2019.rds")

# five counties in new york city
P = nystate %>% 
  filter(COUNTYFIP %in% c(61,47,81,5,85) & 
           (RENT > 0) & 
           (INCTOT > 0) & 
           !(INCTOT %in% c(9999998,9999999))) %>% 
  select(RENT, INCTOT, PUMA, SEX, AGE, RACE, EDUC)

# make age into 5 categories, race into 5 categories, educational attainment into 5 categories, sex as binary variable
P  = P %>% mutate(
  age_fivegroups = cut(
    P$AGE,
    breaks = c(min(P$AGE),21,40,65,80,max(P$AGE)),
    include.lowest = TRUE,
    labels = 1:5),
  race_fivegroups = case_when(RACE == 1 ~ 1,
                              RACE == 2 ~ 2,
                              RACE == 3 ~ 3,
                              RACE %in% c(4,5,6) ~ 4,
                              RACE %in% c(7,8,9) ~ 5),
  edu_fivegroups = case_when(EDUC == 0 ~ 1,
                             EDUC %in% c(1,2) ~ 2,
                             EDUC %in% c(3,4,5,6) ~ 3,
                             EDUC %in% c(7,8,9,10) ~ 4,
                             EDUC == 11 ~ 5),
  sex_binary = case_when(SEX == 1 ~ 0,
                         SEX == 2 ~ 1)
)

# convert covariates to factors 
P$age_fivegroups = as.factor(P$age_fivegroups)
P$race_fivegroups = as.factor(P$race_fivegroups)
P$edu_fivegroups = as.factor(P$edu_fivegroups)


P$index = 1:(dim(P)[1])

P$logRENTcentered = log(P$RENT) - mean(log(P$RENT))

# Dsize is nonrep sample size
Dsize = 1000
# ACSstratasize is the size of random sample in each PUMA strata when performing a stratified random sample of P
ACSstratasize = 10

# get population sizes of PUMA in P
P_PUMAsize = P %>% group_by(PUMA) %>% summarise(N = n()) %>% mutate(fraction = N/sum(N))

# Define probs to do PPSWOR for D2
P$INCTOTprobD2 = 0
P[P$INCTOT<=median(P$INCTOT), c("INCTOTprobD2")] = p
P[P$INCTOT>median(P$INCTOT), c("INCTOTprobD2")] = 1-p

# create response vector for every individual in P as a function of age and sex
P$response_prob = arm::invlogit(0.02*P$AGE + 0.05*P$sex_binary)

# sample D2
D2indices = sample(x=1:dim(P)[1],
                   prob=P$INCTOTprobD2,
                   replace=FALSE,
                   size=Dsize)

D2 = P[D2indices,]

# ACS sample S without inclusion probs and defining incomebracket ####
pseudoACS_unweighted_beforeloop = c()

# Stage 1: Get stratified sample pseudoACS_unweighted, where strata are PUMA. Sampled according to relative size of PUMA
# Stage 2: Now add nonresponse according to P$response_prob
for (PUMA_ in P_PUMAsize$PUMA) {
  pseudoACS_unweighted_beforeloop = rbind(pseudoACS_unweighted_beforeloop,
                                          P %>% filter(PUMA==PUMA_) %>% 
                                            sample_n( size = round((ACSstratasize * 55) * 
                                                                     (P_PUMAsize %>% filter(PUMA==PUMA_) %>% select(fraction) %>% as.numeric)),
                                                      weight = response_prob,
                                                      #weight = 1,
                                                      replace=FALSE
                                            )
  )
}



rm(D2indices,nystate,PUMA_)
gc()

summary(D2$INCTOT)

D2 %>% filter(age_fivegroups==age_fivegroups_target, sex_binary==sex_binary_target) %>% summarise(mean(logRENTcentered), sd(logRENTcentered)/sqrt(n()),n())
P %>% filter(age_fivegroups==age_fivegroups_target, sex_binary==sex_binary_target) %>% summarise(mean(logRENTcentered), sd(logRENTcentered)/sqrt(n()))
```

## Pull in the data and fix things

```{r}
#load("alex_design.RData")

main_survey <- D2 %>% mutate(logRent = RENT, 
                             logINCTOT = log(INCTOT))
population <- P %>% mutate(logRent = RENT, 
                           logINCTOT = log(INCTOT))
aux_survey <- pseudoACS_unweighted_beforeloop %>% 
  mutate(logRent = RENT, 
         logINCTOT = log(INCTOT)) %>%
  left_join(P_PUMAsize, by = "PUMA") %>%
  rename(puma_size = N)
rm(D2, P, pseudoACS_unweighted_beforeloop, P_PUMAsize)
gc()
```

## Do this for a single J

```{r, message = FALSE}
mrp_sd <- function(J, 
                   main_survey_ = main_survey, 
                   aux_survey_ = aux_survey, 
                   population_ = population,
                   target_age_group = age_fivegroups_target,
                   target_sex_binary = sex_binary_target){
  ## make the income_level variable
  main_survey_ <- main_survey_ %>% mutate(
    income_bracket = cut(
      main_survey_$INCTOT,
      breaks=quantile(population_$INCTOT, 
                      probs = seq(0,1,by=1/J)),
      include.lowest = TRUE,
      labels = 1:J)
  )
  
  aux_survey_<- aux_survey_ %>% mutate(
    income_bracket = cut(
      aux_survey_$INCTOT,
      breaks = quantile(population_$INCTOT,
                        probs = seq(0,1,by = 1/J)),
      include.lowest = TRUE,
      labels = 1:J)
  )
    
  
  ## not needed, just for checking against correct Nj
  population_ <- population_ %>% mutate(
    income_bracket = cut(
      population_$INCTOT,
      breaks = quantile(population_$INCTOT,
                        probs = seq(0,1,by = 1/J)),
      include.lowest = TRUE,
      labels = 1:J)
  )
  
  poststrat_true <- right_join((population_ %>% 
                                  group_by(sex_binary,
                                           income_bracket, 
                                           age_fivegroups) %>%
                                  summarise(Nj = n()) %>%
                                  ungroup()
  ),
  tibble(expand.grid(sex_binary = c(0,1),
                     income_bracket = factor(1:J),
                     age_fivegroups = factor(1:5)), zero = 0),
  by = c("sex_binary", "income_bracket", "age_fivegroups"))
  
  poststrat_true$Nj[is.na(poststrat_true$Nj)] = 0
  
  
  ## Estimate Nj_hat from the aux survey and compute covariance matrix
  margins <- population_ %>% group_by(PUMA) %>% summarise(Freq=n())
  margins_sex = population_ %>% group_by(sex_binary) %>% summarise(Freq = n())
  margins_age_fivegroups = population_ %>% group_by(age_fivegroups) %>% summarise(Freq=n())
  
  # initialize aux survey as stratified random sample
  aux_design <- svydesign(id = ~1,
                          strata = ~PUMA,
                          data = aux_survey_,
                          fpc = ~puma_size)
  #aux_design <- svydesign(id = ~1, data=aux_survey_)


  aux_rake <- rake(design = aux_design,
                   list(~PUMA,
                        ~sex_binary,
                        ~age_fivegroups
                   ),
                   list(margins,
                        margins_sex,
                        margins_age_fivegroups
                   ))
  
    # aux_rake <- rake(design = aux_design,
    #                list(~PUMA
    #                ),
    #                list(margins
    #                ))
  

  Nj_hat <- svytotal(~interaction(sex_binary,
                                  income_bracket, 
                                  age_fivegroups),
                     aux_rake)
  gc()
  #Nj_hat <- svytable(~income_bracket + age_fivegroups + edu_fivegroups + race_fivegroups, aux_rake)
  
  Nj_cov <- vcov(Nj_hat)
  
  
  ## We would usually have to do a join here, but there's only one
  ## covariate in the model so we don't!
  # poststrat <- Nj_hat %>%
  #   coef %>%
  #   enframe() %>%
  #   mutate(income_bracket = stringr::str_extract(name, "[0-9]+")) %>%
  #   rename(Nj_hat = value) %>%
  #   select(-name)
  
  poststrat <- Nj_hat %>%
    coef %>%
    enframe %>% mutate(Nj_hat = value)
  
  rm(Nj_hat)
  gc()
  
  poststrat$sex_binary = lapply(str_match_all(poststrat$name,"[0-9]+"), FUN = function(x) {(as.numeric(x))[1]}) %>% unlist
  poststrat$income_bracket = lapply(str_match_all(poststrat$name,"[0-9]+"), FUN = function(x) {(as.numeric(x))[2]}) %>% unlist
  poststrat$age_fivegroups = lapply(str_match_all(poststrat$name,"[0-9]+"), FUN = function(x) {(as.numeric(x))[3]}) %>% unlist

  
  ## Estimate multilevel model
  bye <-capture.output(
  mod <- brm(formula = logRENTcentered ~ sex_binary + (1 | income_bracket) + (1 | age_fivegroups),
             prior = c(
               prior(normal(0, 5), class=Intercept), # change sd to 2
               prior(normal(0, 5), class = sd),
               prior(normal(0, 5), class = sigma),
               prior(normal(0, 5), class = b)
             ),
             data = main_survey_,
             chains=1,
             cores=1,
             refresh = 0,
             backend = "cmdstanr",
             control = list(adapt_delta = 0.95)
            
  ), type = "output")
  gc()
  
  ## Poststrat (both with Nj and Nj_hat just for checking)
  prediction <- posterior_linpred(mod, 
                                  newdata = poststrat,
                                  allow_new_levels = TRUE)
  
  prediction_ps <- apply( prediction, 1, function(x){
    sum(poststrat$Nj_hat * x) / sum(poststrat$Nj_hat)
  })
  
  prediction_ps_true <- apply( prediction, 1, function(x){
    sum(poststrat_true$Nj * x) / sum(poststrat_true$Nj)
  })
  
  
  ## Organise the output
  N <- length(population_$logRENTcentered)
  theta_mean <- colMeans(prediction)
  theta_cov <- cov(prediction)
  
  # Subgroup analysis for age group defined by target_age_group ####
  poststrat$index = 1:dim(poststrat)[1]
  
  subgroup_poststrat_indices = poststrat %>% 
    filter(age_fivegroups == target_age_group, sex_binary == target_sex_binary) %>% 
    select(index) %>% unlist()
  
  # https://cran.r-project.org/web/packages/survey/vignettes/domain.pdf  
  # https://stats.stackexchange.com/questions/411026/why-it-is-important-to-make-survey-design-object-svydesign-function-in-r-with-i
  aux_rake_subset = subset(aux_rake, age_fivegroups == target_age_group & sex_binary == target_sex_binary)
  
  
  Nj_over_N_hat_subpop = svymean(~interaction(sex_binary, income_bracket, age_fivegroups),
                                 aux_rake_subset)
  gc()
  
  # get poststrat proportions for subgroup
  subpop_proportions = Nj_over_N_hat_subpop %>% coef %>% enframe %>% mutate(Nj_over_N_hat = value)
  
  subpop_proportions$sex_binary = lapply(str_match_all(subpop_proportions$name,"[0-9]+"), FUN = function(x) {(as.numeric(x))[1]}) %>% unlist
  subpop_proportions$income_bracket = lapply(str_match_all(subpop_proportions$name,"[0-9]+"), FUN = function(x) {(as.numeric(x))[2]}) %>% unlist
  subpop_proportions$age_fivegroups = lapply(str_match_all(subpop_proportions$name,"[0-9]+"), FUN = function(x) {(as.numeric(x))[3]}) %>% unlist

  subpop_proportions = subpop_proportions %>% filter(age_fivegroups == target_age_group & sex_binary == target_sex_binary)
  
  Nj_over_N_cov = vcov(Nj_over_N_hat_subpop)[subgroup_poststrat_indices, subgroup_poststrat_indices]
  
  
  prediction_subgroup = posterior_linpred(mod, 
                                          newdata = poststrat[subgroup_poststrat_indices,],
                                          allow_new_levels = TRUE)
  
  prediction_ps_subgroup <- apply(prediction_subgroup, 1, function(x){
    sum(poststrat[subgroup_poststrat_indices,]$Nj_hat * x) / sum(poststrat[subgroup_poststrat_indices,]$Nj_hat)
  })
  
  #########
  
  
  prediction_ps_true_subgroup <- apply( prediction_subgroup, 1, function(x){
    sum(poststrat_true[subgroup_poststrat_indices,]$Nj * x) / sum(poststrat_true[subgroup_poststrat_indices,]$Nj)
  })
  
  
  # output what we estimated
  tibble(mean_logRENT = mean(prediction_ps),
         mean_logRENT_true = mean(prediction_ps_true),
         var_logRENT_true = var(prediction_ps_true),
         var_logRENT = var(prediction_ps),
         term1 = sum(diag(theta_cov %*% Nj_cov)) / N^2,
         term2 = (t(poststrat$Nj_hat) %*% theta_cov %*% poststrat$Nj_hat) / N^2,
         term3 = (t(theta_mean) %*% Nj_cov %*% theta_mean) / N^2,
         total = term1 + term2 + term3,
         population_level_var = (summary(mod)[["spec_pars"]][1])^2,
         age_grouplevel_var = (summary(mod)[["random"]]$age_fivegroups[1])^2,
         income_grouplevel_var = (summary(mod)[["random"]]$income_bracket[1])^2,
         maxeigen_theta_cov = max(eigen(theta_cov)$values),
         twonormsquared_poststratweights = sum((poststrat$Nj_hat/sum(poststrat$Nj_hat))^2),
         twonormsquared_poststratweights_known = sum((poststrat_true$Nj/sum(poststrat_true$Nj))^2),
         sharp_upper_bound = maxeigen_theta_cov * twonormsquared_poststratweights,
         
         term1_subgroup = sum(diag(theta_cov[subgroup_poststrat_indices, subgroup_poststrat_indices] %*% Nj_over_N_cov)),
         term2_subgroup = var(prediction_ps_subgroup),
         term3_subgroup = (t(theta_mean[subgroup_poststrat_indices]) %*% Nj_over_N_cov %*% theta_mean[subgroup_poststrat_indices]) / (sum(poststrat[subgroup_poststrat_indices,]$Nj_hat))^2,
         
         maxeigen_theta_cov_subgroup = max(eigen(theta_cov[subgroup_poststrat_indices, subgroup_poststrat_indices])$values),
         twonormsquared_poststratweights_subgroup = sum((poststrat[subgroup_poststrat_indices,]$Nj_hat/sum(poststrat[subgroup_poststrat_indices,]$Nj_hat))^2),
         twonormsquared_poststratweights_known_subgroup = sum((poststrat_true[subgroup_poststrat_indices,]$Nj/sum(poststrat_true[subgroup_poststrat_indices,]$Nj))^2),
         sharp_upper_bound_subgroup = maxeigen_theta_cov_subgroup * twonormsquared_poststratweights_subgroup
         )
}

mrp_sd(10)

```


## Ok now let's run it 

```{r, message = FALSE, warning = FALSE}
#tibble(J = c(3,10,20,30,40,50,60,70,80,90,100))
est <- tibble(J = c(3,10,20,30,40,50,60,70,80,90,100)) %>%
  mutate(out = purrr::map(J, mrp_sd)) %>% 
  unnest(out)

#readr::write_csv(est, path = "dan_est.csv")              
saveRDS(est, file = paste0("est_",
                           seed_num,
                           "_",
                           Dsize,
                           "_",
                           ACSstratasize,
                           "_",
                           p*100,
                           "_",
                           age_fivegroups_target,
                           "_",
                           sex_binary_target,
                           ".rds"))

```

## Make a plot

Notation:

term1: $\frac{1}{N^2}  {\text{tr}} \left( {\Sigma_{\theta \mid \mathcal{D}}} \hat{{\Sigma}}_{J,N} \right)$

term2: $\frac{1}{N^2} \vec{\hat{N}}^T {\Sigma_{\theta \mid \mathcal{D}}} \vec{\hat{N}}$

term3: $\frac{1}{N^2} {\hat{\Theta}_{J}}^T \hat{{\Sigma}}_{J,N} {\hat{\Theta}_{J}}$

maxeigen theta cov: $\lambda_\text{max} \left( \Sigma_{\theta | \mathcal{D}}  \right)$

twonormsquared poststratweights : $|| \frac{\vec{\hat{N}}}{\hat{N}^2} ||_2^2$

twonormsquared poststratweights known: $|| \frac{\vec{{N}}}{{N}^2} ||_2^2$

sharp upper bound: $|| \frac{\vec{\hat{N}}}{\hat{N}^2} ||_2^2 \lambda_\text{max} \left( \Sigma_{\theta | \mathcal{D}}  \right)$

upperbound true: $|| \frac{\vec{{N}}}{{N}^2} ||_2^2 \lambda_\text{max} \left( \Sigma_{\theta | \mathcal{D}}  \right)$

```{r}
est$upperbound_true = est$twonormsquared_poststratweights_known * est$maxeigen_theta_cov
est$upperbound_true_subgroup = est$twonormsquared_poststratweights_known_subgroup * est$maxeigen_theta_cov_subgroup

est %>% pivot_longer(-c(J, mean_logRENT, mean_logRENT_true)) %>% 
  filter(!(name %in% c("age_grouplevel_var",
                       "income_grouplevel_var", 
                       "population_level_var",
                       "var_logRENT",
                       "var_logRENT_true",
                       "term1_subgroup",
                       "term2_subgroup",
                       "term3_subgroup",
                       "maxeigen_theta_cov_subgroup",
                       "twonormsquared_poststratweights_subgroup",
                       "twonormsquared_poststratweights_known_subgroup",
                       "sharp_upper_bound_subgroup",
                       "upperbound_true_subgroup",
                       "total"
                       ))) %>% 
  ggplot(aes(x = J, y = value, colour = name)) +
  geom_line() + scale_y_log10() + 
  ylab("log-scaled variance term") + 
  ggtitle("population estimand")
```

```{r}
est %>% pivot_longer(-c(J, mean_logRENT, mean_logRENT_true)) %>% 
  filter((name %in% c(
                       "term1_subgroup",
                       "term2_subgroup",
                       "term3_subgroup",
                       "maxeigen_theta_cov_subgroup",
                      "twonormsquared_poststratweights_subgroup",
                       "twonormsquared_poststratweights_known_subgroup",
                       "sharp_upper_bound_subgroup",
                       "upperbound_true_subgroup"
                       ))) %>% 
  ggplot(aes(x = J, y = value, colour = name)) +
  geom_line() + scale_y_log10() + 
  ylab("log-scaled variance term") + 
  ggtitle(("subpop estimand"))
```

## A potential reason for why $\frac{1}{\hat{N}^2} \vec{\hat{N}}^T {\Sigma_{\theta \mid \mathcal{D}}} \vec{{\hat{N}}}$ is constant across $J$

The sharp upper bound below is nearly constant across $J$ from the above plot.

$\begin{equation}
        \begin{aligned}
          \frac{1}{\hat{N}^2} \vec{\hat{N}}^T {\Sigma_{\theta \mid \mathcal{D}}} \vec{{\hat{N}}} &\le \left|\left| \frac{\vec{\hat{N}}}{\hat{N}^2} \right|\right|_2^2 \lambda_\text{max} \left( \Sigma_{\theta | \mathcal{D}}  \right)
        \end{aligned}
\end{equation}$

When $\vec{\hat{N}}$ is replaced by $\vec{{N}}$, the upper bound becomes constant.



```{r,eval = FALSE}

# est_1000_15 = readRDS("est_420001_1000_15.rds")
# est_1000_25 = readRDS("est_420001_1000_25.rds")
# est_2000_15 = readRDS("est_420001_4000_15.rds")
# est_2000_25 = readRDS("est_420001_4000_25.rds")
# 
# 
# est_1000_15$upperbound_true = est_1000_15$twonormsquared_poststratweights_known * est_1000_15$maxeigen_theta_cov
# est_1000_15$upperbound_true_subgroup = est_1000_15$twonormsquared_poststratweights_known_subgroup * est_1000_15$maxeigen_theta_cov_subgroup
# 
# est_1000_25$upperbound_true = est_1000_25$twonormsquared_poststratweights_known * est_1000_25$maxeigen_theta_cov
# est_1000_25$upperbound_true_subgroup = est_1000_25$twonormsquared_poststratweights_known_subgroup * est_1000_25$maxeigen_theta_cov_subgroup
# 
# est_2000_15$upperbound_true = est_2000_15$twonormsquared_poststratweights_known * est_2000_15$maxeigen_theta_cov
# est_2000_15$upperbound_true_subgroup = est_2000_15$twonormsquared_poststratweights_known_subgroup * est_2000_15$maxeigen_theta_cov_subgroup
# 
# est_2000_25$upperbound_true = est_2000_25$twonormsquared_poststratweights_known * est_2000_25$maxeigen_theta_cov
# est_2000_25$upperbound_true_subgroup = est_2000_25$twonormsquared_poststratweights_known_subgroup * est_2000_25$maxeigen_theta_cov_subgroup
# 
# 
# est_combined = rbind(tibble(est_1000_15, Dsize = 1000, ACSstratasize = 15*55),
#                      tibble(est_1000_25, Dsize = 1000, ACSstratasize = 25*55),
#                      tibble(est_2000_15, Dsize = 2000, ACSstratasize = 15*55),
#                      tibble(est_2000_25, Dsize = 2000, ACSstratasize = 25*55)
#                      )
# 
# est_combined %>% pivot_longer(-c(J, mean_logRENT, mean_logRENT_true,Dsize,ACSstratasize)) %>% 
#     filter(!(name %in% c("age_grouplevel_var",
#                          "income_grouplevel_var", 
#                          "population_level_var",
#                          "var_logRENT",
#                          "var_logRENT_true",
#                          "term1_subgroup",
#                          "term2_subgroup",
#                          "term3_subgroup",
#                          "maxeigen_theta_cov_subgroup",
#                          "twonormsquared_poststratweights_subgroup",
#                          "twonormsquared_poststratweights_known_subgroup",
#                          "sharp_upper_bound_subgroup",
#                          "upperbound_true_subgroup",
#                          "total","upper_bound_true",
#                          "twonormsquared_poststratweights_known",
#                          "upperbound_true",
#                          "twonormsquared_poststratweights",
#                          "maxeigen_theta_cov"
#     ))) %>% 
#     ggplot(aes(x = J, y = value, colour = name)) +
#     geom_line() + facet_grid(Dsize ~ ACSstratasize) +
#     scale_y_log10() + 
#     ylab("log-scaled variance term") + 
#     ggtitle("population estimand")
# 



est_p90 = readRDS("est_420002_1000_15_90_4_0.rds")
est_p75 = readRDS("est_420002_1000_15_75_4_0.rds")
est_p50 = readRDS("est_420002_1000_15_50_4_0.rds")

est_p90_2000 = readRDS("est_420002_2000_15_90_4_0.rds")
est_p75_2000 = readRDS("est_420002_2000_15_75_4_0.rds")
est_p50_2000 = readRDS("est_420002_2000_15_50_4_0.rds")

est_p90_4000 = readRDS("est_420002_4000_15_90_4_0.rds")
est_p75_4000 = readRDS("est_420002_4000_15_75_4_0.rds")
est_p50_4000 = readRDS("est_420002_4000_15_50_4_0.rds")

est_p90$upperbound_true = est_p90$twonormsquared_poststratweights_known * est_p90$maxeigen_theta_cov
est_p90$upperbound_true_subgroup = est_p90$twonormsquared_poststratweights_known_subgroup * est_p90$maxeigen_theta_cov_subgroup
est_p90$total_subgroup = rowSums(est_p90[,c("term1_subgroup",
                                            "term2_subgroup",
                                            "term3_subgroup"
)])

est_p75$upperbound_true = est_p75$twonormsquared_poststratweights_known * est_p75$maxeigen_theta_cov
est_p75$upperbound_true_subgroup = est_p75$twonormsquared_poststratweights_known_subgroup * est_p75$maxeigen_theta_cov_subgroup
est_p75$total_subgroup = rowSums(est_p75[,c("term1_subgroup",
                                            "term2_subgroup",
                                            "term3_subgroup"
)])

est_p50$upperbound_true = est_p50$twonormsquared_poststratweights_known * est_p50$maxeigen_theta_cov
est_p50$upperbound_true_subgroup = est_p50$twonormsquared_poststratweights_known_subgroup * est_p50$maxeigen_theta_cov_subgroup
est_p50$total_subgroup = rowSums(est_p50[,c("term1_subgroup",
                                            "term2_subgroup",
                                            "term3_subgroup"
)])


est_p90_2000$upperbound_true = est_p90_2000$twonormsquared_poststratweights_known * est_p90_2000$maxeigen_theta_cov
est_p90_2000$upperbound_true_subgroup = est_p90_2000$twonormsquared_poststratweights_known_subgroup * est_p90_2000$maxeigen_theta_cov_subgroup
est_p90_2000$total_subgroup = rowSums(est_p90_2000[,c("term1_subgroup",
                                                      "term2_subgroup",
                                                      "term3_subgroup"
)])

est_p75_2000$upperbound_true = est_p75_2000$twonormsquared_poststratweights_known * est_p75_2000$maxeigen_theta_cov
est_p75_2000$upperbound_true_subgroup = est_p75_2000$twonormsquared_poststratweights_known_subgroup * est_p75_2000$maxeigen_theta_cov_subgroup
est_p75_2000$total_subgroup = rowSums(est_p75_2000[,c("term1_subgroup",
                                                      "term2_subgroup",
                                                      "term3_subgroup"
)])

est_p50_2000$upperbound_true = est_p50_2000$twonormsquared_poststratweights_known * est_p50_2000$maxeigen_theta_cov
est_p50_2000$upperbound_true_subgroup = est_p50_2000$twonormsquared_poststratweights_known_subgroup * est_p50_2000$maxeigen_theta_cov_subgroup
est_p50_2000$total_subgroup = rowSums(est_p50_2000[,c("term1_subgroup",
                                                      "term2_subgroup",
                                                      "term3_subgroup"
)])

est_p90_4000$upperbound_true = est_p90_4000$twonormsquared_poststratweights_known * est_p90_4000$maxeigen_theta_cov
est_p90_4000$upperbound_true_subgroup = est_p90_4000$twonormsquared_poststratweights_known_subgroup * est_p90_4000$maxeigen_theta_cov_subgroup
est_p90_4000$total_subgroup = rowSums(est_p90_4000[,c("term1_subgroup",
                                                      "term2_subgroup",
                                                      "term3_subgroup"
)])

est_p75_4000$upperbound_true = est_p75_4000$twonormsquared_poststratweights_known * est_p75_4000$maxeigen_theta_cov
est_p75_4000$upperbound_true_subgroup = est_p75_4000$twonormsquared_poststratweights_known_subgroup * est_p75_4000$maxeigen_theta_cov_subgroup
est_p75_4000$total_subgroup = rowSums(est_p75_4000[,c("term1_subgroup",
                                                      "term2_subgroup",
                                                      "term3_subgroup"
)])

est_p50_4000$upperbound_true = est_p50_4000$twonormsquared_poststratweights_known * est_p50_4000$maxeigen_theta_cov
est_p50_4000$upperbound_true_subgroup = est_p50_4000$twonormsquared_poststratweights_known_subgroup * est_p50_4000$maxeigen_theta_cov_subgroup
est_p50_4000$total_subgroup = rowSums(est_p50_4000[,c("term1_subgroup",
                                                      "term2_subgroup",
                                                      "term3_subgroup"
)])

est_combined = rbind(tibble(est_p90, Dsize = 1000, ACSstratasize = 15*55, p = "Very nonrepresentative"),
                     tibble(est_p75, Dsize = 1000, ACSstratasize = 15*55, p = "Nonrepresentative"),
                     tibble(est_p50, Dsize = 1000, ACSstratasize = 15*55, p = "Representative"),
                     tibble(est_p90_2000, Dsize = 2000, ACSstratasize = 15*55, p = "Very nonrepresentative"),
                     tibble(est_p75_2000, Dsize = 2000, ACSstratasize = 15*55, p = "Nonrepresentative"),
                     tibble(est_p50_2000, Dsize = 2000, ACSstratasize = 15*55, p = "Representative"),
                     tibble(est_p90_4000, Dsize = 4000, ACSstratasize = 15*55, p = "Very nonrepresentative"),
                     tibble(est_p75_4000, Dsize = 4000, ACSstratasize = 15*55, p = "Nonrepresentative"),
                     tibble(est_p50_4000, Dsize = 4000, ACSstratasize = 15*55, p = "Representative")
)

est_combined$p = factor(est_combined$p)
est_combined$p = factor(est_combined$p, levels = c("Representative",
                                                   "Nonrepresentative",
                                                   "Very nonrepresentative"))

colnames(est_combined)[colnames(est_combined)=="term1"] = "Variance term 1"
colnames(est_combined)[colnames(est_combined)=="term2"] = "Variance term 2"
colnames(est_combined)[colnames(est_combined)=="term3"] = "Variance term 3"
colnames(est_combined)[colnames(est_combined)=="sharp_upper_bound"] = "Upper bound"
colnames(est_combined)[colnames(est_combined)=="p"] = "Main survey data type"

colnames(est_combined)[colnames(est_combined)=="total"] = "Total"



# est_combined %>% pivot_longer(-c(J, mean_logRENT, mean_logRENT_true,Dsize,ACSstratasize,p)) %>% 
#     filter(!(name %in% c("age_grouplevel_var",
#                          "income_grouplevel_var", 
#                          "population_level_var",
#                          "var_logRENT",
#                          "var_logRENT_true",
#                          "term1_subgroup",
#                          "term2_subgroup",
#                          "term3_subgroup",
#                          "maxeigen_theta_cov_subgroup",
#                          "twonormsquared_poststratweights_subgroup",
#                          "twonormsquared_poststratweights_known_subgroup",
#                          "sharp_upper_bound_subgroup",
#                          "upperbound_true_subgroup",
#                          "total","upper_bound_true",
#                          "twonormsquared_poststratweights_known",
#                          "upperbound_true",
#                          "twonormsquared_poststratweights",
#                          "maxeigen_theta_cov"
#     ))) %>% 
#     ggplot(aes(x = J, y = value, colour = name)) +
#     geom_line(size=0.8) + facet_grid(Dsize~p) +
#     scale_y_log10() + 
#     ylab("log-scaled variance term") + 
#     ggtitle("") + 
#     theme_minimal() +
#     theme(legend.position="bottom",
#           legend.box="vertical",
#           text = element_text(size=20),
#           axis.text.x = element_text(angle=45, hjust=1),
#           strip.text.x = element_text(size = 20),
#           strip.text.y = element_text(size = 20),
#           legend.title = element_text(size = 20),
#           panel.spacing = unit(2, "lines")
#     ) + labs(color='')
# 
# ggsave(paste0("population_3_100.png"), width = 15, height = 12)





est_combined %>% pivot_longer(-c(J, mean_logRENT, mean_logRENT_true,Dsize,ACSstratasize,`Main survey data type`)) %>% 
  filter(!(name %in% c("age_grouplevel_var",
                       "income_grouplevel_var", 
                       "population_level_var",
                       "var_logRENT",
                       "var_logRENT_true",
                       "term1_subgroup",
                       "term2_subgroup",
                       "term3_subgroup",
                       "maxeigen_theta_cov_subgroup",
                       "twonormsquared_poststratweights_subgroup",
                       "twonormsquared_poststratweights_known_subgroup",
                       "sharp_upper_bound_subgroup",
                       "upperbound_true_subgroup",
                       "total_subgroup",
                       "twonormsquared_poststratweights_known",
                       "upperbound_true",
                       "twonormsquared_poststratweights",
                       "maxeigen_theta_cov"
  ))) %>% 
  ggplot(aes(x = J, y = value, colour = name)) +
  geom_line(size=1,aes(linetype=`Main survey data type`)) + facet_grid(.~Dsize) +
  scale_y_log10() + 
  ylab("log-scaled variance term") + 
  ggtitle("") + 
  theme_minimal() +
  theme(legend.position="bottom",
        legend.box="vertical",
        text = element_text(size=25),
        axis.text.x = element_text(angle=45, hjust=1),
        strip.text.x = element_text(size = 25),
        strip.text.y = element_text(size = 25),
        legend.title = element_text(size = 25),
        panel.spacing = unit(2, "lines")
  ) + labs(color='Variance term') + scale_colour_manual(values=c("Total"="#D55E00",
                                                                 "Upper bound" = "#56B4E9",
                                                                 "Variance term 1"= "#009E73",
                                                                 "Variance term 2"="#0072B2",
                                                                 "Variance term 3"="#CC79A7"))

ggsave(paste0("population_3_100.png"), width = 24, height = 12)






colnames(est_combined)[colnames(est_combined)=="term1_subgroup"] = "Variance term 1 subgroup"
colnames(est_combined)[colnames(est_combined)=="term2_subgroup"] = "Variance term 2 subgroup"
colnames(est_combined)[colnames(est_combined)=="term3_subgroup"] = "Variance term 3 subgroup"
colnames(est_combined)[colnames(est_combined)=="sharp_upper_bound_subgroup"] = "Upper bound subgroup"
colnames(est_combined)[colnames(est_combined)=="total_subgroup"] = "Total subgroup"




est_combined %>% pivot_longer(-c(J, mean_logRENT, mean_logRENT_true,Dsize,ACSstratasize,`Main survey data type`)) %>% 
  filter(!(name %in% c("age_grouplevel_var",
                       "income_grouplevel_var", 
                       "population_level_var",
                       "var_logRENT",
                       "var_logRENT_true",
                       "Variance term 1",
                       "Variance term 2",
                       "Variance term 3",
                       "maxeigen_theta_cov_subgroup",
                       "twonormsquared_poststratweights_subgroup",
                       "twonormsquared_poststratweights_known_subgroup",
                       "sharp_upper_bound_subgroup",
                       "upperbound_true_subgroup",
                       "Total",
                       "twonormsquared_poststratweights_known",
                       "upperbound_true",
                       "twonormsquared_poststratweights",
                       "maxeigen_theta_cov",
                       "Upper bound"
  ))) %>% 
  ggplot(aes(x = J, y = value, colour = name)) +
  geom_line(size=1, aes(linetype=`Main survey data type`)) + facet_grid(.~Dsize) +
  scale_y_log10() + 
  ylab("log-scaled variance term") + 
  ggtitle("") + 
  theme_minimal() +
  theme(legend.position="bottom",
        legend.box="vertical",
        text = element_text(size=25),
        axis.text.x = element_text(angle=45, hjust=1),
        strip.text.x = element_text(size = 25),
        strip.text.y = element_text(size = 25),
        legend.title = element_text(size = 25),
        panel.spacing = unit(2, "lines")
  ) + labs(color='Variance term') + scale_colour_manual(values=c("Total subgroup"="#D55E00",
                                                                 "Upper bound subgroup" = "#56B4E9",
                                                                 "Variance term 1 subgroup"= "#009E73",
                                                                 "Variance term 2 subgroup"="#0072B2",
                                                                 "Variance term 3 subgroup"="#CC79A7"))

ggsave(paste0("subpopulation_0_4_3_100.png"), width = 24, height = 12)
```


