---
title: "Prior and Posterior Predictive checks"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This RMD file produces Figure 1 in Chapter 4 of my PhD thesis: When should we collapse cells for Multilevel Regression and Poststratification?

## Posterior predictive check for $J = 12$ income brackets where response is RENT, for representative dataset of size 2000, $D_1$

```{r,echo=FALSE}
library(tidyverse)
library(brms)
library(tidybayes)
library(survey)
library(bayesplot)

# v1 contains logRENTcentered

# get NY state 
# https://data.census.gov/cedsci/table?q=United%20States&g=0400000US36&y=2019&tid=ACSST1Y2019.S0101
#nystate = ddi %>% filter(STATEFIP==36)
nystate = readRDS("nystate_fiveyear2015_2019.rds")


J = 3
Dsize = 1000

#### STEP 1: CREATE TARGET POPULATION P #####
# TARGET POPULATION P has covariate INCTOT and true values RENT. PUMA is used to perform stratified sampling
# The ppl of NY county are used 
# OUTPUT: P as a dataframe, estimand as average log rent in P.


# P is New York City without survey weights
# COUNTYFIP: 61=New York county, 47=Kings county, 81=Queens county, 5=Bronx county, 85=Richmond county
P = nystate %>% 
  filter(COUNTYFIP %in% c(61,47,81,5,85) & RENT > 0 & (INCTOT > 0) & !(INCTOT %in% c(9999998,9999999))) %>% 
  select(RENT, INCTOT, PUMA)

P$logRENTcentered = log(P$RENT) - mean(log(P$RENT))

# get population sizes of PUMA in P
P_PUMAsize = P %>% group_by(PUMA) %>% summarise(N = n())

# Define probs to do PPSWOR for D1,D2,D3
P$INCTOTprobD1 = 0
P[P$INCTOT<=median(P$INCTOT), c("INCTOTprobD1")] = 0.5
P[P$INCTOT>median(P$INCTOT), c("INCTOTprobD1")] = 0.5
P$INCTOTprobD2 = 0
P[P$INCTOT<=median(P$INCTOT), c("INCTOTprobD2")] = 0.75
P[P$INCTOT>median(P$INCTOT), c("INCTOTprobD2")] = 0.25
P$INCTOTprobD3 = 0
P[P$INCTOT<=median(P$INCTOT), c("INCTOTprobD3")] = 0.9
P[P$INCTOT>median(P$INCTOT), c("INCTOTprobD3")] = 0.1

# P$INCTOTprobD3 = 0
# P[P$INCTOT<=20000, c("INCTOTprobD3")] = 0.9
# P[P$INCTOT>20000, c("INCTOTprobD3")] = 0.1


# create J incomebrackets in target population P
P$incomebracket = cut(P$INCTOT,
                      breaks=quantile(x=P$INCTOT, probs = seq(0,1, by=1/J)),
                      include.lowest = TRUE
)

# rename incomebracket levels
levels(P$incomebracket) = 1:J


# sample D1
D1indices = sample(x=1:dim(P)[1],
                   prob=P$INCTOTprobD1,
                   replace=FALSE,
                   size=Dsize)

D1 = P[D1indices,]
# sample D2
D2indices = sample(x=1:dim(P)[1],
                   prob=P$INCTOTprobD2,
                   replace=FALSE,
                   size=Dsize)

D2 = P[D2indices,]
# sample D3
D3indices = sample(x=1:dim(P)[1],
                   prob=P$INCTOTprobD3,
                   replace=FALSE,
                   size=Dsize)

D3 = P[D3indices,]
```

```{r}
# Posterior predictive check D1
model_D1_check_log = brm(formula = logRENTcentered ~ (1|incomebracket),
               prior = c(
                 prior(normal(0, 5), class=Intercept), 
                 prior(normal(0, 5), class = sd),
                 prior(normal(0, 5), class = sigma)
               ),
               data = D1,
               chains=1,
               cores=1,
               #control = list(adapt_delta = 0.95), 
               #sample_prior="only"
               )

yrep_fit_posterior_D1_log <- posterior_predict(model_D1_check_log)

#complete_yrep_fit_posterior=yrep_fit_posterior_D1[complete.cases(yrep_fit_posterior_D1),]

# 200 prior simulations
complete_yrep_fit_posterior_f_D1_log=yrep_fit_posterior_D1_log[1:200,]

# below is from bayesplot
ppc_dens_overlay(D1$logRENTcentered,
                 complete_yrep_fit_posterior_f_D1_log) +
  xlab("log(RENT)") + ylab("Density") + ggtitle("Posterior predictive check D1")
```



```{r}
# prior predictive check D1
model_D1_check_log = brm(formula = logRENTcentered ~ (1|incomebracket),
               prior = c(
                 prior(normal(0, 5), class=Intercept), 
                 prior(normal(0, 5), class = sd),
                 prior(normal(0, 5), class = sigma)
               ),
               data = D1,
               chains=1,
               cores=1,
               control = list(adapt_delta = 0.95), 
               sample_prior="only"
               )

yrep_fit_posterior_D1_log <- posterior_predict(model_D1_check_log)

#complete_yrep_fit_posterior=yrep_fit_posterior_D1[complete.cases(yrep_fit_posterior_D1),]

# 200 prior simulations
complete_yrep_fit_posterior_f_D1_log=yrep_fit_posterior_D1_log[1:200,]

# below is from bayesplot
ppc_dens_overlay(D1$logRENTcentered,
                 complete_yrep_fit_posterior_f_D1_log) +
  xlab("log(RENT)") + ylab("Density") + ggtitle("Prior predictive check D1")
```

# Prior/Posterior predictive check for $J = 12$ income brackets where response is logRENTcentered, for nonrepresentative dataset $D_3$

```{r}
# Posterior predictive check

model_D3_check_log = brm(formula = logRENTcentered ~ (1|incomebracket),
               prior = c(
                 prior(normal(0, 5), class=Intercept), 
                 prior(normal(0, 5), class = sd),
                 prior(normal(0, 5), class = sigma)
               ),
               data = D3,
               chains=1,
               cores=1,
               control = list(adapt_delta = 0.95), 
               #sample_prior="only"
               )

yrep_fit_posterior_D3_log <- posterior_predict(model_D3_check_log)

#complete_yrep_fit_posterior=yrep_fit_posterior_D3[complete.cases(yrep_fit_posterior_D3),]

# 200 prior simulations
complete_yrep_fit_posterior_f_D3_log=yrep_fit_posterior_D3_log[1:200,]

# below is from bayesplot
ppc_dens_overlay(D3$logRENTcentered,
                 complete_yrep_fit_posterior_f_D3_log) +
  xlab("log(RENT)") + ylab("Density") + ggtitle("Posterior predictive check D3") 

D3_posteriorpredictivecheck = ppc_dens_overlay(D3$logRENTcentered,
                                               complete_yrep_fit_posterior_f_D3_log) +
  xlab("log-Rent") + ylab("Density") + ggtitle("Posterior predictive check D3") +
  ggtitle("") +
  theme_minimal() +
  theme(legend.position="bottom",
        legend.box="vertical",
        text = element_text(size=25),
        axis.text.x = element_text(angle=45, hjust=1),
        strip.text.x = element_text(size = 25),
        strip.text.y = element_text(size = 25),
        legend.title = element_text(size = 25),
        panel.spacing = unit(2, "lines")
  ) + xlim(c(-3,3))
  # xlim(c(min(D3$logRENTcentered),
  #        max(D3$logRENTcentered)))



```


```{r}
# Prior predictive check

model_D3_check_log = brm(formula = logRENTcentered ~ (1|incomebracket),
               prior = c(
                 prior(normal(0, 5), class=Intercept), 
                 prior(normal(0, 5), class = sd),
                 prior(normal(0, 5), class = sigma)
               ),
               data = D3,
               chains=1,
               cores=1,
               control = list(adapt_delta = 0.95), 
               sample_prior="only"
               )

yrep_fit_posterior_D3_log <- posterior_predict(model_D3_check_log)

#complete_yrep_fit_posterior=yrep_fit_posterior_D3[complete.cases(yrep_fit_posterior_D3),]

# 200 prior simulations
complete_yrep_fit_posterior_f_D3_log=yrep_fit_posterior_D3_log[1:200,]

# below is from bayesplot
ppc_dens_overlay(D3$logRENTcentered,
                 complete_yrep_fit_posterior_f_D3_log) +
  xlab("log(RENT)") + ylab("Density") + ggtitle("Prior predictive check D3") 

D3_priorpredictivecheck = ppc_dens_overlay(D3$logRENTcentered,
                                           complete_yrep_fit_posterior_f_D3_log) +
  xlab("log-Rent") + ylab("Density") + ggtitle("Prior predictive check D3")  +
  ggtitle("") +
  theme_minimal() +
  theme(legend.position="bottom",
        legend.box="vertical",
        text = element_text(size=25),
        axis.text.x = element_text(angle=45, hjust=1),
        strip.text.x = element_text(size = 25),
        strip.text.y = element_text(size = 25),
        legend.title = element_text(size = 25),
        panel.spacing = unit(2, "lines")
  ) + xlim(c(-3,3))
  # xlim(c(min(D3$logRENTcentered),
  #        max(D3$logRENTcentered)))


cowplot::plot_grid(D3_priorpredictivecheck, D3_posteriorpredictivecheck,
                   labels = c("Prior predictive check", "Posterior predictive check"),
                   label_size = 25)

ggsave(paste0("D3_ppd.png"), width = 20, height = 10)
```
